Maximum Entropy Spectral Analysis: a case study

### 2024-02-12 paper/mesa.tex
added and corrected affiliations

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TITLE
	\title{Maximum Entropy Spectral Analysis: a case study}
	\author{Alessandro \surname{Martini}\inst{\ref{inst1}}\thanks{martini.alessandr@gmail.com} \and 
	Stefano \surname{Schmidt}\inst{\ref{inst2}}\thanks{s.schmidt@uu.nl} \and Gregory \surname{Ashton}\inst{\ref{inst1}}\thanks{walter.delpozzo@unipi.it} \and Walter \surname{Del Pozzo}\inst{\ref{inst1}}\thanks{walter.delpozzo@unipi.it}}

        \institute{Dipartimento di Fisica  Università di Pisa, and INFN Sezione di Pisa, Pisa I-56127,Italy\label{inst1} \and Institute for Gravitational and Subatomic Physics (GRASP),Utrecht University, Princetonplein 1, 3584 CC, Utrecht, The Netherlands\label{inst2}}

@@

\section{Full posterior distribution for GW150914} \label{sec:appendix_b}
\begin{figure}
	\caption{Full posterior distribution for GW150914 when marginalising over the AR process orders.}
	\label{fig:gw150914_full_pe}
	\includegraphics[width=\textwidth,keepaspectratio]{Images/gw150914/mega_plot.pdf}
\end{figure}
\end{appendix}

>>>>

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TITLE
	\title{Maximum Entropy Spectral Analysis: a case study}
	\author{Alessandro \surname{Martini}\inst{1,2,3}\thanks{alessandro.martini-1@unitn.it} \and 
	Stefano \surname{Schmidt}\inst{4,5}\thanks{s.schmidt@uu.nl} \and Gregory \surname{Ashton}\inst{6} \and Walter \surname{Del Pozzo}\inst{1}\thanks{walter.delpozzo@unipi.it}}

        \institute{Dipartimento di Fisica  Università di Pisa, and INFN Sezione di Pisa, Pisa I-56127,Italy
        		      \and Università di Trento, Dipartimento di Fisica, I-38123 Povo, Trento, Italy
		      \and INFN, Trento Institute for Fundamental Physics and Applications, I-38123 Povo, Trento, Italy
        		      \and Institute for Gravitational and Subatomic Physics (GRASP),Utrecht University, Princetonplein 1, 3584 CC, Utrecht, The Netherlands
		      \and Nikhef, Science Park 105, 1098 XG, Amsterdam, The Netherlands
		      \and Royal Holloway University of London, London, United Kingdom}

@@

\section{Full posterior distribution for GW150914} \label{sec:appendix_b}
\begin{figure*}
	\caption{Full posterior distribution for GW150914 when marginalising over the AR process orders.}
	\label{fig:gw150914_full_pe}
	\includegraphics[width=\textwidth,keepaspectratio]{Images/gw150914/mega_plot.pdf}
\end{figure*}
\end{appendix}
